Clustering: A pipeline to analyse time-course gene expression data

### 2019-04-24 scripts/03_clustering.Rmd
ENH adding model explorer

---
title: "Clustering: A pipeline to analyse time-course gene expression data"
output: rmarkdown::html_vignette
---

```{r echo=FALSE, results="hide"}
# Loading dependencies
library(devtools)
library(limma)
library(splines)
library(stats)
library(moanin)
source("utils.R")
# library(moanin)
```

@@

    - *Within cluster similarity as a function of the number of cluster* XXX
      Elbow method
    - *Silhouette method* 
    - *Stability analysis*: this method assumes that the results of the
      clustering will be more stable for the "true" number of clusters than
      for other number of clusters.

@@

@@

>>>>

---
title: "Clustering: A pipeline to analyse time-course gene expression data"
output: rmarkdown::html_vignette
bibliography: bibliography.bib
---

```{r echo=FALSE, results="hide", message=FALSE}
# Loading dependencies
library(devtools)
library(limma)
library(splines)
library(stats)
library(moanin)
library(NMF)
source("utils.R")
# library(moanin)
```

@@

    - Elbow method
    - *Silhouette method* 
    - *Model explorer*

@@

The last strategy is to look at the stability of the clustering.

@@

```{r}
n_clusters = 5:20
all_labels = list()
for(i in n_clusters){
    filename = paste0("results/stability_", i, ".tsv")
    stability = read.table(filename, sep="\t")
    all_labels[[paste0("C", i)]] = stability
}
```

```{r fig.width=8, fig.height=8}
library(moanin)
moanin::plot_model_explorer(all_labels)
```
